Age-related changes in plant growth and traits

### 2015-04-28 results_growth.Rmd
mostly looking at growth patterns

source("scripts/summary_dataframes.R")
```
#RV curves and RA schedules, general patterns

@@

#RV curves
```{r, echo=FALSE,message=FALSE}
plot(ReproInv~FinalWeight, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(ReproInv~FinalWeight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

plot((1+ReproInv_mean)~FinalWeight_mean,SummarySppAge,log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "ReproInv"
xvar <- "FinalWeight"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="xy", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#RV curves (by age)
```{r, echo=FALSE,message=FALSE}
plot(ReproInv~age, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend(15,5000,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot((1+ReproInv_mean)~age,SummarySppAge,log="xy", col=col.spp[as.factor(species)],pch=16)
legend(15,5000,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "ReproInv"
xvar <- "age"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="xy", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#RA schedules (by age)
```{r, echo=FALSE,message=FALSE}
plot(RA~age, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
legend(15,.9,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(RA_mean~age,SummarySppAge,log="x", col=col.spp[as.factor(species)],pch=16)
legend(15,.5,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "RA"
xvar <- "age"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#RA schedules (by size)
```{r, echo=FALSE,message=FALSE}
plot(RA~FinalWeight, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(RA_mean~FinalWeight_mean,SummarySppAge,log="x", col=col.spp[as.factor(species)],pch=16)
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "RA"
xvar <- "FinalWeight"

data <- SummaryInd
data <- split(data, data$species)

lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#Reproductive Investment by Growth Investment
```{r, echo=FALSE,message=FALSE}
plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

plot((1+ReproInv_mean)~GrowthInv_mean,SummarySppAge,log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "ReproInv"
xvar <- "GrowthInv"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="xy", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#RA by Growth Investment
```{r, echo=FALSE,message=FALSE}
plot(RA~GrowthInv, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(RA~GrowthInv, SummaryInd, log="x", col=col.age[as.factor(age)],pch=16)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

plot(RA_mean~GrowthInv_mean,SummarySppAge,log="x", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "RA"
xvar <- "GrowthInv"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#Reproductive Investment by scaled height 
For these calculations, height is scaled relative to max height. This should be a way to determine RSOM - RSOM would be the PropH at which Reproductive Investment begins.

```{r, echo=FALSE, message=FALSE}
plot((1+ReproInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot((1+ReproInv)~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "PropH"
xvar <- "ReproInv"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]]+1)))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

```{r, echo=FALSE, message=FALSE}
plot((RA~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(RA~PropH, SummaryInd, col=col.age[as.factor(age)],pch=16)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "RA"
xvar <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#Growth Investment versus proportion max H
This turns out to be one of the most interesting sets of graphs
For the canopy species, PELA, HATE, PEPU, BAER, investment in growth plateaus (i.e. growth relative to size decreases) at ~40% maxH
For the shorter and shorter-lived species there is much less of a relationship, or a complete lack of relationship (i.e. BOLE, PHPH)
Quite interesting, there is a distinctly negative relationship for GRBU
For many of the species with a good relationship, it seems that there are two breakpoints in the curve - wondering what these mean with respect to reproductive onset and RA

```{r, echo=FALSE, message=FALSE}
plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(GrowthInv~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "GrowthInv"
xvar <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

These plots show very clearly that for all species RGR suddenly dips when RA becomes non-zero. Plotting against "FinalWeight" or "GrowthInvestment" is much less clear - in other words, an individual's height is the best way to sort them into plants investing more in growth vs reproduction. There are of course some non-reproductive plants with "PropH" above the obvious cut-off, but these are almost certainly "reproductively mature" plants not reproducing in a given year.

The canopy species have, not suprisingly, a very obvious maxH, with Growth Investment or RGR tapering markedly at the maxH is approached. In these species growth investment is poorly correlated with RA, but well correlated with height.
In some of the mid-height species (GRSP, BOLE, GRBU), growth investment is very poorly correlated with height, but well correlated with RA - in other words, increased RA = less growth.
Some species are correated with neither.

Now my current analyses still lack the ability to tease apart the most obvious pattern - because I don't actually want to show that growth and height are correlated, so much as that the asymptoting of growth is correlated with height - i.e. the change in slope of the relationship.

```{r, echo=FALSE, message=FALSE}
yvar <- "GrowthInv"
xvar <- "RA"
x2var <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])+(x[[x2var]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                    main=spp, xlab=xvar, ylab=yvar)
  abline(lmfits[[spp]])
}
```

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="BOLE"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="GRBU"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="GRSP"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PELA"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="HATE"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="BAER"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PEPU"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="EPMI"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="LEES"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PHPH"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PUTU"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="HEPU"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PILI"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="COER"))
summary(mod)
anova(mod)
```{r, echo=FALSE, message=FALSE}
plot((RGR~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "RGR"
xvar <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)
  abline(lmfits[[spp]])
}
```

#Plotting RGR and RA vs. proportion maxH and simply RA vs RGR

```{r, echo=FALSE, message=FALSE}
plot(RGR~PropH,data=subset(SummaryInd, species=="BAER"),pch=16, col="black")
points((5*RA)~PropH,data=subset(SummaryInd, species=="BAER"),pch=16, col="red")

plot(RGR~PropH,data=subset(SummaryInd, species=="HATE"),pch=16, col="black")
points((10*RA)~PropH,data=subset(SummaryInd, species=="HATE"),pch=16, col="red")

plot(RGR~PropH,data=subset(SummaryInd, species=="EPMI"),pch=16, col="black")
points((5*RA)~PropH,data=subset(SummaryInd, species=="EPMI"),pch=16, col="red")

plot(RGR~PropH,data=subset(SummaryInd, species=="PEPU"),pch=16, col="black")
points((3*RA)~PropH,data=subset(SummaryInd, species=="PEPU"),pch=16, col="red")

plot(RGR~PropH,data=subset(SummaryInd, species=="BOLE"),pch=16, col="black")
points((3*RA)~PropH,data=subset(SummaryInd, species=="BOLE"),pch=16, col="red")

plot((1/RGR)~(RA),SummaryInd,log="y",col=col.spp[as.factor(species)],pch=16)
plot((RGR)~(RA),data=subset(SummaryInd,species=="BOLE"),log="y",col=col.spp[as.factor(species)],pch=16)
mod <- lm(RA~log(RGR),data=subset(SummaryInd,species=="BOLE"))
summary(mod)

yvar <- "GrowthInv"
xvar <- "RA"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                    main=spp, xlab=xvar, ylab=yvar)
  abline(lmfits[[spp]])
}

>>>>

source("scripts/summary_dataframes.R")
```
#Growth data, general patterns

@@

```{r, echo=FALSE, message=FALSE}
yvar <- ""
xvar <- ""
data <- filter(SummaryInd,

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar)

summary(mod)
anova(mod)
```

```{r, echo=FALSE, message=FALSE}

```

### 2015-04-28 results_leaf_lifespan.rmd
mostly looking at growth patterns

#Leaf lifespan data
General results:

@@

```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "LL_birth"
xvar <- "LL_death"
data <- filter(SummaryInd, age>2, LL_birth<10&LL_death<10)

@@

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar, ,col=col.spp[as.factor(data$species)])
legend("bottomright",legend=labels.spp,pch=16,col=col.spp,bty="n",cex=.8)
mod <- lm(LL_birth~LL_bd,data=data)
summary(mod)

@@

#Starting with the basics: Are leaf lifespan and LMA correlated?
Plotting species*site means
Figures shown using all three measures of leaf lifespan
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "LMA_mean"
xvar <- "LL_death_mean"
data <- filter(SummarySppAge)

@@

#Same plots as above, but omitting HATE, which has much higher LMA than any other species due to its round "leaves"
Using leaf deaths gives the poorest fit...
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "LMA_mean"
xvar <- "LL_death_mean"
data <- filter(SummarySppAge, species!="HATE")

@@

Age is log transformed.
BAER, HEPU, PUTU show a significant DECREASE in leaf lifespan with increasing age (p<0.05)
LEES, PEPU shows a marginally significant DECREASE in accessory costs with increasing age (0.05<p<0.10)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "LL_death"
xvar <- "age"
data <- filter(SummaryInd,LL_death<10&age>2)

@@

If leaf lifespan based on leaf births is used instead, there are a number of significant INCREASES in leaf lifespan with increasing size
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "LL_death"
xvar <- "FinalWeight"
data <- filter(SummaryInd,LL_death<8&age>2)

@@

```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "LL_death"
xvar <- "GrowthInv"
data <- filter(SummaryInd,LL_death<8&age>2)

@@

#Putting age and speices together in a model shows, not surprisingly, that both age and species contribute to the variation and that species matters much more.
```{r, echo=FALSE,results='hide', message=FALSE}
plot(LL_death ~ age, data=SummaryInd, cex.axis=.8, las=1, xlim=c(1,35), ylim=c(.95,10), log="xy", pch=16,col=col.spp[as.factor(species)])
legend(14,8,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

```{r, echo=FALSE,results='hide', message=FALSE}
plot(LL_death ~ lvs_end_total, data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

```{r, echo=FALSE,results='hide', message=FALSE}
mod <- lm(LMA_mean~species*age, SummarySppAge)
summary(mod)
anova(mod)

@@

The interactions terms weren't significant and were removed from the model
```{r, echo=FALSE,results='hide', message=FALSE}
mod <- lm(LMA_mean~species+log(FinalWeight_mean), SummarySppAge)
summary(mod)
anova(mod)

@@

```{r, echo=FALSE,results='hide', message=FALSE}

>>>>

#Leaf lifespan data
General results:
  - Leaf lifespan increases from seedlings (1.4 yrs) to saplings (2.4 years) to adults (>4 years), but there are no differences between the different adult populations
  - Species differ en

@@

```{r, echo=FALSE, message=FALSE}
yvar <- "LL_birth"
xvar <- "LL_death"
data <- filter(SummaryInd, age>2, LL_birth<10&LL_death<10)

@@

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar,col=col.spp[as.factor(data$species)])
legend("bottomright",legend=labels.spp,pch=16,col=col.spp,bty="n",cex=.8)
mod <- lm(LL_birth~LL_bd,data=data)
summary(mod)

@@

#Starting with the basics: Are leaf lifespan and LMA correlated?
Plotting species*site means
Figures shown using all three measures of leaf lifespan
```{r, echo=FALSE,message=FALSE}
yvar <- "LMA_mean"
xvar <- "LL_death_mean"
data <- filter(SummarySppAge)

@@

#Same plots as above, but omitting HATE, which has much higher LMA than any other species due to its round "leaves"
Using leaf deaths gives the poorest fit...
```{r, echo=FALSE,message=FALSE}
yvar <- "LMA_mean"
xvar <- "LL_death_mean"
data <- filter(SummarySppAge, species!="HATE")

@@

Age is log transformed.
BAER, HEPU, PUTU show a significant DECREASE in leaf lifespan with increasing age (p<0.05)
LEES, PEPU shows a marginally significant DECREASE in accessory costs with increasing age (0.05<p<0.10)
```{r, echo=FALSE,message=FALSE}
yvar <- "LL_death"
xvar <- "age"
data <- filter(SummaryInd,LL_death<10&age>2)

@@

If leaf lifespan based on leaf births is used instead, there are a number of significant INCREASES in leaf lifespan with increasing size
```{r, echo=FALSE,message=FALSE}
yvar <- "LL_death"
xvar <- "FinalWeight"
data <- filter(SummaryInd,LL_death<8&age>2)

@@

```{r, echo=FALSE,message=FALSE}
yvar <- "LL_death"
xvar <- "GrowthInv"
data <- filter(SummaryInd,LL_death<8&age>2)

@@

#Putting age and speices together in a model shows, not surprisingly, that both age and species contribute to the variation and that species matters much more.
```{r, echo=FALSE,message=FALSE}
plot(LL_death ~ age, data=SummaryInd, cex.axis=.8, las=1, xlim=c(1,35), ylim=c(.95,10), log="xy", pch=16,col=col.spp[as.factor(species)])
legend(14,8,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

```{r, echo=FALSE,message=FALSE}
plot(LL_death ~ lvs_end_total, data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

```{r, echo=FALSE,message=FALSE}
mod <- lm(LMA_mean~species*age, SummarySppAge)
summary(mod)
anova(mod)

@@

The interactions terms weren't significant and were removed from the model
```{r, echo=FALSE,message=FALSE}
mod <- lm(LMA_mean~species+log(FinalWeight_mean), SummarySppAge)
summary(mod)
anova(mod)

@@

```{r, echo=FALSE,message=FALSE}
